Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations

### 2024-09-27 main.tex
changes: Sobolev vector fields, potentials, nonlinear reflection

% Added by MV 
\usepackage{bm} % preferred version of bold symbols
\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
\usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
\setlength{\marginparwidth}{2cm}

@@

We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
We already know the optimal constants for the gradient operator over convex domains,
and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.

For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
and the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
% 
In comparison to their work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, which are of independent interest. 
\\

In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $D > 0$.

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator. 
\\

We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
In order to analyze the properties of the potential operators,
we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
    .
\end{align*}
If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq D$, which gives 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{D} r^{n-k-1} \,dr 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
\end{align*}
We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.

We begin with the Poincar\'e operator. 
Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
    \left| \Poinc_{\ell} u(x) \right|
    \left| 
        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
We recall the radial integrals 
    \int_{B_D(0)} |z|^{k+1-n} \,dz
    \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} \,dr
    \vol_{n-1}(S_1) \int_{0}^{D} r^{k} \,dr
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
We compute 
    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{n-\ell}$. 
In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\ell} u(x)$ pointwise by 
    \left| \Bogov_{\ell} u(x) \right|
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
%     \int_{B_D(0)} |z|^{k+1-n} dz
%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k+1-n} r^{n-1} dr
%     \vol_{n-1}(S_1) \int_{0}^{D} r^{k} dr
%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
% We compute 
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{\ell-1}$. 
In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{\vol(\Omega)} 
    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_D(0)) D$. 
Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 

@@

We are in the position to establish the main results of this section.
This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
though the dimension and the form degree enters the estimate.

\begin{theorem}
    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}\Alt^{\ell-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
        D
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{\vol(\Omega)} 
        D
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}
\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.

@@

@@

MWL appreciates helpful remarks by Abdellatif Aitelhad and by Martin Costabel.

>>>>

% Added by MV 
\usepackage{bm} % preferred version of bold symbols
\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
\newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
\setlength{\marginparwidth}{2cm}

@@

{\color{red}
We want to bound Poincar\'e--Friedrichs constants for the exterior derivative over convex domains.
We already know the optimal constants for the gradient operator over convex domains,
and we know bounds for the Poincar\'e--Friedrichs constants for the entire $L^{2}$ de~Rham complex. 
We are not aware of such bounds for the case of the $L^{p}$ de~Rham complex when $1 \leq p \leq \infty$.

For that reason, we bound the norms of regularized potential operators for the exterior derivative over convex domains.
We solve this for two special cases: either the $L^{p}$ de~Rham complex without boundary conditions, 
and the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudodifferential operators over domains star-shaped with respect to a ball. 
% 
In comparison to their work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, which are of independent interest.

In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.
}

We \cye{now give} bounds for Poincar\'e--Friedrichs constants for the exterior derivative over convex domains\cye{, in} two special cases\todo{MV: Discussion already in the introduction, or in Remark~\ref{remark:reg_Poinc_Bog}}: 
either the $L^{p}$ de~Rham complex without boundary conditions, \cye{or} the $L^{p}$ de~Rham with full boundary conditions. 
The corresponding potential operators are known as the regularized Poincar\'e and regularized Bogovski\u{\i} potentials in the literature. 
We build upon the discussion spearheaded by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who analyze them as pseudo\cye{-}differential operators over domains star-shaped with respect to a ball. 
In comparison to their work, our discussion is more modest:
we study potential operators merely over convex sets, and we are only interested in their operator norms between Lebesgue spaces.
However, our purpose are explicit bounds for the operator norms, \cye{giving the Poincar\'e--Friedrichs constants}. Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open\todo{MV: Weakly Lipschitz??} set with diameter $\cye{\diam(\Omega)} > 0$\todo{MV: Unifying the notation.}.

\subsection{Regularized Poincar\'e and Bogovski\u{\i} operators}

We begin with introducing the Costabel-McIntosh kernel.
For any $\ell \in \{0,\dotsc,n\}$, we define the kernel $G_{\ell} : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}\label{math:mainkernel}
  G_{\ell}(x,y) = \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} \vol(\Omega)^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt
  .
\end{equation}
Given a differential form $u \in {C^\infty_c}(\bbR^n,\Alt^\ell)$, where \(1 \leq \ell \leq n\), 
we then define the integral operators
\begin{align*}
  \Poinc_{\ell} u(x) &= \int_{\Omega} G_{n-\ell+1}(y,x) \,(x-y)\lrcorner u(y)\,dy,
  \\
  \Bogov_{\ell} u(x) &= \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy.
\end{align*}
We call $\Poinc_{\ell}$ the Poincar\'e operator and $\Bogov_{\ell}$ the Bogovski\u{\i} operator.

We show that the integrals in the definition of $\Poinc_{\ell}$ and $\Bogov_{\ell}$ actually exist. 
In order to analyze the properties of the potential operators,
we first rewrite the Costabel-McIntosh kernel $G_{\ell}$.
Letting $x,y \in \bbR^n$ with $x \neq y$, we find 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \int_{0}^{\infty} t^{n-\ell} (t+1)^{\ell-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-\ell+k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{\ell-1-k} t^{n-\ell+\ell-1-k} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \int_{0}^{\infty} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega} \left( x+t(x-y) \right)\,dt
    \\
    &= 
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \int_{0}^{\infty} t^{n-k-1} \vol(\Omega)^{-1} \chi_{\Omega}\left( x+t(x-y) \right)\,dt 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \, |x-y|^{k-n} \int_{0}^{\infty} r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr
    .
\end{align*}
If $x, y \in \Omega$, then we can restrict the inner integrals to the range $0 \leq r \leq \diam(\Omega)$, which gives 
\begin{align*}
    G_{\ell}(x,y) 
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_{0}^{\diam(\Omega)} r^{n-k-1} \,dr 
    \\
    &= 
    \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ \diam(\Omega)^{n-k} }{n-k}.
\end{align*}
We are now in a position to show that the potentials are bounded with respect to Lebesgue norms.

\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}

We begin with the Poincar\'e operator. 
Let $B_{\diam(\Omega)}(0)$ be the $n$-dimensional ball centered at the origin.
Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_{\diam(\Omega)}(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
    &
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} \,dr
    \\&
    =
    \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} \,dr
    =
    \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
    ,
\end{align*}
where $S_1 \subseteq \bbR^{n}$ stands for the unit sphere of dimension $n-1$. 
We compute 
\begin{align}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
    \label{equation:A_Poinc}
    .
\end{align}
Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{n-\ell}$. 
In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\ell} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{k} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{k+1}}{k+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \int_{B_{\diam(\Omega)}(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ \diam(\Omega)^{n-k} }{n-k} \frac{\diam(\Omega)^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
    \label{equation:A_Bogov}
    .
\end{align*}
Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{\ell-1}$. 
In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}\Alt^{\ell-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) \vol(\Omega)^{-1} \vol_{n}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

\subsection{Additional properties}

@@

\subsection{Operator norms as bounds for the Poincar\'e--Friedrichs constants}

\mwl{We are in the position to establish the main results of this section.
Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.
This includes upper bounds for the Poincar\'e--Friedrichs inequalities that we have been looking for. 
Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
though the dimension and the form degree enters the estimate.}

We now state the main results of this section. \cye{Recall that $\cye{\diam(\Omega)} > 0$ is the diameter of $\Omega$ and that $B_{\cye{\diam(\Omega)}}(0)$ is the $n$-dimensional ball centered at the origin.} The \cye{following} upper bounds for the Poincar\'e--Friedrichs \cye{constants} \cye{are} proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
though the \cye{space} dimension \cye{$n$} and the form degree \cye{$\ell$} enter\cye{\sout{s}} the estimate\cye{s, namely through definitions~\eqref{equation:A_Poinc} and~\eqref{equation:A_Bogov} of respectively $A_{\Poinc}(n,\ell)$ and $A_{\Bogov}(n,\ell)$}.

\begin{theorem}\label{theorem:PF_EC}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}\Alt^{\ell-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}

\todo[inline]{MV: Do $\Poinc_{\ell}$ and $\Bogov_{\ell}$ still map piecewise polynomials to piecewise polynomials? Like Raviart--Thomas and N\'ed\'elec spaces to Raviart--Thomas and N\'ed\'elec spaces??}\mwl{No, they do not respect any piecewise structure.}

\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.

@@

\mwl{TODO: Illustration}

@@

MWL appreciates helpful remarks by Abdellatif Aitelhad, by Martin Costabel, and by John M.\ Lee.
